---
title: "Business Intelligence Project"
author: "<Allan Mwandawiro>"
date: "<10/09/2023>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |                   |
|----------------------------------------------|-------------------|
| **Student ID Number**                        | 135372...         |
| **Student Name**                             | Allan Mwandawiro. |
| **BBIT 4.2 Group**                           | A                 |
| **BI Project Group Name/ID (if applicable)** | Wisdom            |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset

### Source:

The dataset that was used can be downloaded here: [*https://archive.ics.uci.edu/dataset/544/estimation+of+obesity+levels+based+on+eating+habits+and+physical+condition*](https://archive.ics.uci.edu/dataset/544/estimation+of+obesity+levels+based+on+eating+habits+and+physical+condition){.uri}

### Reference:

*\<*

```         
Estimation of obesity levels based on eating habits and physical condition . (2019). UCI Machine Learning Repository. https://doi.org/10.24432/C5H31Z.
```

*\>\
Refer to the APA 7th edition manual for rules on how to cite datasets: <https://apastyle.apa.org/style-grammar-guidelines/references/examples/data-set-references>*

```{r Dataset Loader}
library(readr)
ObesityDataSet_raw_and_data_sinthetic <- read_csv("data/estimation+of+obesity+levels+based+on+eating+habits+and+physical+condition/ObesityDataSet_raw_and_data_sinthetic.csv")
View(ObesityDataSet_raw_and_data_sinthetic)

# Provide the executable R code inside the various code chunks as guided by the lab work.
```

...to be continued
